Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification

### 2019-08-07 190410_Paper_ACPR/paper_v4.tex
siamkar: make spectrogram

In recent years, several behavioral biometric traits for identity authentication have been investigated in view of their rigid physical body independence~\cite{bailador2011analysis}. Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is taking considerable interest with the development of the in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}. % more in-air ref
With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than contact-based authentication systems.

@@

Case I: Table~\ref{tab3} shows the best average EER performance from five runs of two-fold cross-validation test and the parameter condition. Among the linear methods, the SVM with RBF kernel function showed best verification performance of 24.31\% EER followed by the SVM with Linear kernel function. However, all three deep learning based methods showed better performance than the SVM with RBF kernel function since the deep learning based methods can utilize the original size (500 $\times$ 30 $\times$ 6) of the input data in the training stage.

>>>>

In recent years, several behavioral biometric traits for identity authentication have been investigated in view of their rigid physical body independence~\cite{bailador2011analysis}. Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is taking considerable interest with the development of the in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than contact-based authentication systems.

@@

Case I: Table~\ref{tab3} shows the best average EER performance from five runs of two-fold cross-validation test and the parameter condition. Among the linear methods, the SVM with RBF kernel function showed best verification performance of 24.31\% EER followed by the SVM with Linear kernel function. However, all three deep learning based methods showed better performance than the SVM with RBF kernel function since the deep learning based methods can utilize the original size (500$\times$30$\times$6) of the input data in the training stage.
